---
title: "Visualizing output from freeze-dryer"
author: "Casper Sahl Poulsen"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
always_allow_html: yes
output:
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    toc: yes
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = "center")
```

## Introduction 
#### Study headline:
Visualize output from CoolSafe 9L Freeze-dryer https://www.labogene.com/CoolSafe-4-15L-Freeze-Dryers  
Freeze-drying: Primary drying 17h at 0.1hPa and 23 °C. Secondary drying 3h at 0.05hPa and 23 °C.

#### Background:  
In this context it is processing samples from the DCH-NG cohort (Investigations on the interaction between the microbiome, host genetic variation and life style in the development of type 2 diabetes, cardiovascular disease, liver disease and colorectal cancer) limited to MAX. 
Project F2: MAX samples where individuals have collected fecal samples at multiple time points, N=1319.   
Participant and study information is available in a separate document provided by KB.    
Sample aliquoting is performed from freeze-dried specimens. Sample aliquotation is not feasible using traditional laborious methods such as drilling.   

#### Aim:   
Visualize output, primarily investigate if freeze-drying is performing according to planned by achieving a steady temperature. 

### Packages  
```{r}

```

### Reading in data
```{r}


```

## Analysis



## Additional
### Session information
```{r session_info}
sessionInfo()
```

### This document was processed on: 
```{r}
Sys.Date()
```

